---
title: "Stock Forecaster Pitch"
author: "Will Wright"
date: "October 22, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The Problem

Since the dawn of the stock market, financial analysts have struggled to forecast how stock values will change. They were plagued with the inaccuracies of their neolithic forecasting technologies and continually failed to make great predictions, but no longer...

## The Solution

Now, with the advent of the Stock Forecaster, financial analysts can rejoice in using the most advanced forecasting technology!  

How it works:

- Users input any stock ticker
- This ticker is pasted into a URL string where the tokens have been decoded
- Data is pulled directly from Yahoo Finance's servers into R
- Using a Damped Holt-Winters' Additive Model, a forecast is generated

## The Code (pt1)

```{r, echo = TRUE, message = FALSE, warning = FALSE}
    stock<-"GM" #example
    library(fpp)
    library(xts)
    # The Yahoo URL tokens for start month, day, and year are "a=", 
    #  "b=", and "c=", respectively
    end_year<-substr(Sys.Date(),1,4)
    end_month<-as.character(as.integer(substr(Sys.Date(),6,7))-1)
    end_day<-substr(Sys.Date(),9,10)
    start_year<-"1900"; start_month<-"0"; start_day<-"0"
    freq <- "m"
    stock_url <- paste("http://chart.finance.yahoo.com/table.csv?s=",
        stock,"&a=",start_month,"&b=",start_day,"&c=",start_year,
                       "&d=",end_month,"&e=",end_day,"&f=",end_year,
        "&g=",freq,"&ignore=.csv", sep = "")
    stock_data_full<-read.table(stock_url, header = T, sep = ",")
    ```
    
## The Code (pt2)

```{r, echo = TRUE, message = FALSE, warning = FALSE}    
    stock_data <- stock_data_full[,c(1,7)]
    stock_data$Date<-as.Date(stock_data$Date)
    # convert to time series and set start date to 1 with freq = 12 so 
    # hw() can see the seasonality
    stock_ts <- ts(rev(stock_data$Adj.Close), start = 1, frequency = 12)
    #plot(hw(stock_ts, seasonality = "mult", damped = TRUE), 
    #     xlab = "Years Since IPO", ylab = "Closing Price")
```

## The Forecast, Example for General Motors (GM)

```{r}
plot(hw(stock_ts, seasonality = "mult", damped = TRUE), xlab = "Years Since IPO", ylab = "Closing Price")
```

